### 2015-09-29 untitled.tex
edited untitled.tex

Figure \ref{fig:example} is the resulting schedule by using the period enforcer algorithm. The first job of task $\tau_2$ (that arrives at time $0$) is executed as if there is no period enforcement. The second job (that releases at time $11$) of task $\tau_2$ requires some attention to understand how the period enforcer algorithm works. Note that the first computation segment of task $\tau_2$ does not suffer from any deferrable execution (it is postponed due to higher-priority block). Therefore, it is always placed to the ready queue and scheduled as early as possible.

Let's now look at the computation segment $C_2^2$ of the second job of task $\tau_2$. This segment is placed back to the ready queue at time $19$ after its self-suspension. Without period enforcer, this computation segment should be executed from $19$ to $20$. However, the period enforcer algorithm intentionally defers this computation segment to ensure \emph{the periodic demand} of the computation segment $C_2^2$. Therefore, this computation segment is \emph{activated} to the ready queue at time $9+T_2=9+11=20$. This results in a deadline miss.\footnote{By using the notations in \cite{Raj:suspension1991}, we have $ET_{2,1}^2=9, ET_{2,2}^2 = \max\{9+11, 19\}=20$. The superscript $^2$ is for denoting the second computation segment of task $\tau_2$.}

Therefore, the above example shows that there exists (at least) a sporadic segmented self-suspending task system that is schedulable under fixed-priority scheduling without any enforcement, but the corresponding schedule by using period enforcer algorithm is not feasible. In this example, it is also clear that we can pessimistically convert the two computation segments of task $\tau_2$ into two deferrable tasks $\tau_2^1$ and $\tau_2^2$. The deferrable time of task $\tau_2^1$ is $0$, whereas the deferrable time of task $\tau_2^2$ is at most \emph{$9$}. With the above conversion, we can clearly see that the deferrable task set $\{\tau_1, \tau_2^1, \tau_2^2\}$ is in fact not schedulable by the rate-monotonic priority assignment since we can release a job of $\tau_1$ together with a job of $\tau_2^2$ (after its worst-case deferrable time).

>>>>

Figure \ref{fig:example} is the resulting schedule by using the period enforcer algorithm. The first job of task $\tau_2$ (that arrives at time $0$) is executed as if there is no period enforcement. The second job (that releases at time $11$) of task $\tau_2$ requires some attention to understand how the period enforcer algorithm works. Note that the first computation segment of task $\tau_2$ does not suffer from any deferrable execution (it is postponed due to higher-priority block). Therefore, it is always placed to the ready queue immediately when it arrives and scheduled as early as possible.

Let's now look at the computation segment $C_2^2$ of the second job of task $\tau_2$. This segment is placed back to the ready queue at time $19$ after its self-suspension. Without period enforcement, this computation segment should be executed from $19$ to $20$. However, the period enforcer algorithm intentionally defers this computation segment to ensure \emph{the periodic demand} of the computation segment $C_2^2$. Therefore, this computation segment is \emph{activated} to the ready queue at time $9+T_2=9+11=20$. This results in a deadline miss.\footnote{By using the notations in \cite{Raj:suspension1991}, we have $ET_{2,1}^2=9, ET_{2,2}^2 = \max\{9+11, 19\}=20$. The superscript $^2$ is for denoting the second computation segment of task $\tau_2$.}

Therefore, the above example shows that there exists (at least) a sporadic segmented self-suspending task system that is schedulable under fixed-priority scheduling without any enforcement, but the corresponding schedule by using the period enforcer algorithm is not feasible. In this example, it is also clear that we can pessimistically convert the two computation segments of task $\tau_2$ into two deferrable tasks $\tau_2^1$ and $\tau_2^2$. The deferrable time of task $\tau_2^1$ is $0$, whereas the deferrable time of task $\tau_2^2$ is at most \emph{$9$}. With the above conversion, we can clearly see that the deferrable task set $\{\tau_1, \tau_2^1, \tau_2^2\}$ is in fact not schedulable by the rate-monotonic priority assignment since we can release a job of $\tau_1$ together with a job of $\tau_2^2$ (after its worst-case deferrable time).
